SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2021-01-21 maintex.tex
merged table1 into maintex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{deluxetable*}{cccccccccc}
%\tablestypesize{\small} \tablewidth{0pt}
%\tablecaption{Pair Catalog}
%\tablehead{
%\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
%\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
%\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
%}
%\decimals
%\startdata
%7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
%7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
%7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
%7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
%7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
%8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
%8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
%8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
%8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
%8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
%\enddata
%\tablecomments{
%(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) 
%stellar mass. \\ \\
%(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
%}
%\label{tab:pair}
%\end{deluxetable*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{table1.tex}

>>>>

\begin{table}
\begin{center}
\caption{Close Galaxy Pairs and Multiples in MaNGA IFUs}
\label{tab:coords}
\begin{tabular}{lc ccc}
\hline
\hline
Plate-IFU & Index & R.A. (J2000) & Decl. (J2000) & Redshift \\
          &           & (deg)        & (deg)         &     \\
\hline
 7443-12703&0&229.5255758&+42.7458538&0.04043\\
    \nodata&1&229.5265348&+42.7440666&0.04079\\
  7958-3701&0&257.5338400&+33.5989046&0.11015\\
    \nodata&1&257.5344200&+33.5984600&0.10920\\
    \nodata&2&257.5326566&+33.5979470&0.11031\\
  7960-3701&0&257.0857469&+31.7469109&0.10819\\
    \nodata&1&257.0850100&+31.7470300&0.10800\\
  7960-3702&0&258.2893316&+31.5820375&0.02961\\
    \nodata&1&258.2913540&+31.5812244&0.02943\\
  7962-3702&0&259.0637432&+28.0140065&0.10725\\
    \nodata&1&259.0639447&+28.0130439&0.10753\\
\hline
\end{tabular}
\end{center}
\tablecomments{
This table lists a total of 404 plate-IFUs that contain close galaxy pairs and multiples in the eighth MaNGA Product Launch (MPL-8). The second column lists the component index, where ``0'' indicates the primary target of the MaNGA observation. For each IFU, all components within $\pm$2000\,km~s$^{-1}$ of the primary are listed, sorted in ascending angular distance from the primary.\\
(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
}
\end{table}
